Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-10-04 DryDep.tex
Corrected typo.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with MACC-reanalysis}
\label{subsec:macc}
In this section, we conclude the comparison of our results with respect to global ozone by looking at ECWMF's MACC-reanalysis \citep[][data obtained from \href{https://apps.ecmwf.int/datasets/data/macc-reanalysis/levtype=ml/}{ECWMF's data center}]{MACC-II}.
In Fig,~\ref{fig:macc_o3conc}, we compare \emph{mOSaic} ozone concentrations in the lowermost model level with surface concentrations deduced from the MACC-reanalysis for the year 2005. The MACC-reanalysis displays low ozone concentrations above all land masses except for the Greenland ice sheet. The lowest values are found in the deep tropics (e.g. northern South America and central Africa), while the highest values occur within $(25-60)\,\unit{^\circ N}$ over the oceans. These low values over the oceans are relatively well reproduced by \emph{mOSaic} ($\pm 20\,\unit{\%}$). Over, e.g., South America, central and southern Africa, the Arabian peninsula, and the north-western Indian subcontinent, the ozone concentrations are elevated by up to $200\,\unit{\%}$.
Regarding the global average surface ozone concentration, \emph{Wesely\_type} (Supplement S.8) is more consistent with the MACC-reanalysis than \emph{mOSaic}, but shows the same tendency of enhanced ozone over the continents as the latter.
This enhancement is apparent mostly in the deep tropics and over the north-western Indian subcontinent which coincide with regions of high intensity in incoming UV radiation. This may indicated an imbalance in the photo-chemical production and loss of \chem{O_3} in the Oslo~CTM3.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with MACC-reanalysis}
\label{subsec:macc}
In this section, we conclude the comparison of our results with respect to global ozone by looking at ECWMF's MACC-reanalysis \citep[][data obtained from \href{https://apps.ecmwf.int/datasets/data/macc-reanalysis/levtype=ml/}{ECWMF's data center}]{MACC-II}.
In Fig,~\ref{fig:macc_o3conc}, we compare \emph{mOSaic} ozone concentrations in the lowermost model level with surface concentrations deduced from the MACC-reanalysis for the year 2005. The MACC-reanalysis displays low ozone concentrations above all land masses except for the Greenland ice sheet. The lowest values are found in the deep tropics (e.g. northern South America and central Africa), while the highest values occur within $(25-60)\,\unit{^\circ N}$ over the oceans. These low values over the oceans are relatively well reproduced by \emph{mOSaic} ($\pm 20\,\unit{\%}$). Over, e.g., South America, central and southern Africa, the Arabian peninsula, and the north-western Indian subcontinent, the ozone concentrations are elevated by up to $200\,\unit{\%}$.
Regarding the global average surface ozone concentration, \emph{Wesely\_type} (Supplement S.8) is more consistent with the MACC-reanalysis than \emph{mOSaic}, but shows the same tendency of enhanced ozone over the continents as the latter.
This enhancement is apparent mostly in the deep tropics and over the north-western Indian subcontinent which coincides with regions of high intensity in incoming UV radiation. This may indicated an imbalance in the photo-chemical production and loss of \chem{O_3} in the Oslo~CTM3.
